Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-31 main.tex
20180831-02

\section{Photovoltaic Array} \label{array}
In this paper, we use the following model of PV arrays, modules, strings and panels as showed in Fig. \ref{fig1}. A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels. A PV panel is formed by three PV modules (\textit{$N_M=3$}).
% connected in series with bypass diodes. 
And each bypass diode is connected in parallel with a module.
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{PV arrays, strings, and panels.}
\label{fig1}
\end{figure}

@@

We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}. That algorithm will analyzes the panel \textit{I-V} curve sample by finding almost-constant-current and voltage regions and coordinate multiple maximum or minimum power point in the \textit{P-V} curve if PV array is working in mismatched conditions or not.

All the panels in PV array have the same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}. Those parameters can be directly estimated by the prosess provided in\cite{b7}.

Furthermore, it is also assumed that for each string it has same number of panels. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.

\section{Reconfiguration Algorithm} \label{algo}
\subsection{Overview of the algorithm}
In this section, we describe the overview of the reconfiguration algorithm in \cite{b10}. First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}\cite{b9}. As an example, we consider a PV panel where nine panels are connected in three strings. We assume that, in this example, the reconfiguration algorithm finds MPPs given in Table \ref{tab1}.
%To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings. In this example, mismatching conditions presented in Table \ref{tab1}. 
%Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}. As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}. 
After that, the reconfiguration algorithm generates candidates of current assignments, where the current assignment specifies a current of each string. The reconfiguration algorithm treats the current of each MPP as a current candidate for string, and constructs a current assignment by assigning a current candidate to each string. The reconfiguration algorithm generates current assignments by considering all combinations of current candidates for string.
%Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. 
Then, for each current assignment, the reconfiguration algorithm computes the number of working modules in each string. We define a configuration as a combination of a current assignment and the number of working modules in each string. By this algorithm, we obtain a set of candidate configurations. Since we can estimate the generated power of each candidate configuration, we can select the candidate configuration that maximizes the generated power.
%\vspace{10cm}
%Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates. Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array. 
The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{flowchart.png}}
\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
\label{flowchart}
\end{figure}
The previous estimation can not give precise 
\subsection{Feasibility Problem}
Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations. Our proposed algorithm based on the method in \cite{b10} to calculate MPP candidates and using unique panel selection technology to give optimal reconfiguration solution among partial-shading PV array.

In this example, though the procedure in Fast reconfiguration strategy, MPP candidates are presented in (\ref{mpp}) and number of working modules in MPP candidates are presented in (\ref{qmn}), respectively.

\begin{table}[htbp]
\caption{}
\begin{center}
\begin{tabular}{cccc}
\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{equation}
\begin{aligned}
\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
\end{aligned}\label{mpp}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
\end{aligned}
\label{qmn}
\end{equation}

\subsection{Feasibility}
The feasibility of configuration based on the assumption of section \ref{array}, each string in PV array must have same number of panels. Definition of feasibility in (\ref{feas}). When a configuration needs panels in a string (\textit{$NP_n$}) are over maximum number of panels per-string(\textit{$NP_{stMAX}$}) this configuration is unfeasible. 
\begin{equation}
\left\{\begin{matrix}
NP_n > NP_{stMAX}& & \text{Unfeasible}\\ 
NP_n \leq NP_{stMAX} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}
For the first MPP candidate \{0.5, 0.5, 2\} need 8 modules for each string. According to Table \ref{tab1}, for a string current on 2A at least need 4 panels and didn't meet feasible requirement, thus, algorithm terminate. The second MPP candidate \{0.5, 2, 2\} as same as previous one also not feasible.

\subsection{Panel Selection Strategy} \label{selection strategy}
%Calculate MPP candidates based on existed reconfiguration method in \cite{b10}. MPP current candidates and MPP voltage candidates are present in (\ref{e1}) and (\ref{e2}), respectively. Additional, number of real working module at MPP current candidates are given in (\ref{e3}). Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm in \cite{b10}, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
%\begin{equation}
%\begin{aligned}
%\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
%\end{aligned}
%\end{equation}

 In order to give more precise reconfiguration strategy. Our proposed algorithm firstly sort panels in a particular order for MPP candidates. For the example of fourth MPP candidate \{2, 2, 3\}, by giving dataset in Table \ref{tab1} generate a selection matrix in (\ref{mpp3-1}) that each column indicate panel's number and  each row indicate to string number. Element in the matrix corresponding to number of module which be able to working on string current.
\begin{equation}
%\begin{center}
\begin{tabular}{l|lllllllll}
    & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & P9 \\ \hline
St1 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
St2 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
St3 & 0  & 2  & 0  & 0  & 0  & 0  & 1  & 0  & 1 
\end{tabular}\label{mpp3-1}
%\end{center}
\end{equation}
Then calculate number of module difference among string currents. For panel 1, difference between string 3 and string 2 is 1 (\textit{$Diff_1=1$}) and difference between string 2 and string 1 is 0 (\textit{$Diff_2=0$}). Sort panels in lexicographic order by \textit{$Diff_1$} and \textit{$Diff_2$}. As showed in matrix (\ref{sorted}). 
\begin{equation}
\begin{tabular}{l|lllllllll}
        & P2 & P3 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
St1     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
St2     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
St3     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
\textit{$Diff_1$} & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
\textit{$Diff_2$} & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0 
\end{tabular}\label{sorted}
\end{equation}
To find the best PV configuration, following steps are required:
\begin{enumerate} [1-]
\item Select panels in matrix (\ref{sorted}) from left side to right.
\item If the element in matrix is 0, release corresponding panel
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. As the example of string 2, selected panels are [Panel 1, Panel 5], these panels contain modules are equal to next unselect panel [Panel 4]. Then swap [Panel 1, Panel 5] and [Panel4], release [Panel 1, Panel 5]. \label{replace}
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, set unselect panel to a string with minimum length. 
\end{enumerate}
\subsection{Panel Replace Strategy}
In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel. Based on section \ref{array}, each panel only contain three identical PV modules. So the element in selection matrix in the range of 0 to 3. The replacement policy follows priorities are:
\begin{enumerate} [ (1) ]
\item Swap a panel contain 3 working modules to \textbf{three} panels each contain 1 working module.
\item Swap a panel contain 3 working modules to \textbf{one} panel contain 1 working module and \textbf{one} contain 2 working modules.
\item Swap a panel contain 2 working modules to \textbf{two} panels each contain 1 working module.
\end{enumerate}

>>>>

\section{Photovoltaic Array} \label{array}
In this paper, we use the following model of PV arrays, modules, strings and panels as showed in Fig. \ref{fig1}. A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels. A PV panel is formed by three PV modules.
% connected in series with bypass diodes. 
And each bypass diode is connected in parallel with a module.
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{PV arrays, strings, and panels.}
\label{fig1}
\end{figure}

@@

%We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}. That algorithm will analyzes the panel \textit{I-V} curve sample by finding almost-constant-current and voltage regions and coordinate multiple maximum or minimum power point in the \textit{P-V} curve if PV array is working in mismatched conditions or not. 
In mismatched conditions, the power versus voltage (P-V) curve of each panel shows multiple MPPs (maximal power points). We refer to a MPP by a pair $(V_{mpp},I_{mpp})$ where $V_{mpp}$ and $I_{mpp}$ are the voltage and the current that give a maximal power, respectively. The algorithm in \cite{b6} analyzes the current versus voltage (I-V) curves of panels and finds MPPs of each panel in mismatched conditions.
%All the panels in PV array have the same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}. Those parameters can be directly estimated by the prosess provided in\cite{b7}.

%Furthermore, it is also assumed that for each string it has same number of panels. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.

\section{Reconfiguration Algorithm} \label{algo}

\subsection{Overview of the algorithm}
In this section, we describe the overview of the Fast reconfiguration algorithm in \cite{b10}. First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}\cite{b9}. As an example, we consider a PV panel where nine panels are connected in three strings. We assume that, in this example, the reconfiguration algorithm finds MPPs given in Table \ref{tab1}.
%To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings. In this example, mismatching conditions presented in Table \ref{tab1}. 
%Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}. As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}. 
After that, the reconfiguration algorithm generates candidates of current assignments, where the current assignment specifies a current of each string. The reconfiguration algorithm treats the current of each MPP as a current candidate for string, and constructs a current assignment by assigning a current candidate to each string. The reconfiguration algorithm generates current assignments by considering all combinations of current candidates for string.
%Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. 
Then, for each current assignment, the reconfiguration algorithm computes the number of working modules in each string. We define a configuration as a combination of a current assignment and the number of working modules (\textit{$Q_{M_n}$}) in each string. MPP candidates are presented in (\ref{mpp}) and number of working modules of MPP candidates are presented in (\ref{qmn}), respectively.

\begin{equation}
\begin{aligned}
\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
\end{aligned}\label{mpp}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
\end{aligned}
\label{qmn}
\end{equation}
By this algorithm, we obtain a set of candidate configurations. Since we can estimate the generated power of each candidate configuration, we can select the candidate configuration that maximizes the generated power.
%\vspace{10cm}
%Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates. Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array. 
The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{flowchart.png}}
\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
\label{flowchart}
\end{figure}
The previous estimation can not give precise reconfiguration answer. This algorithm lists some candidate configurations ( in addition to the maximum one ) and for each candidate configuration it will executes a time consuming and precise power simulation. Considering there are some errors in previous estimation, this algorithm is not efficient for finding the best configuration. 
\begin{table}[htbp]
\caption{}
\begin{center}
\begin{tabular}{cccc}
\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\subsection{Feasibility Problem}
To execute a power simulation, we have to assign panels to each string to realize a candidate configuration. However, the way is not given in \cite{b10} and some candidate configurations are infeasible. For an configuration example \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string. According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings.Of course we can compute it by using an exhaustive search. However, it is time-consuming. So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.

%Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations. Our proposed algorithm based on the method in \cite{b10} to calculate MPP candidates and using unique panel selection technology to give optimal reconfiguration solution among partial-shading PV array.

%In this example, though the procedure in Fast reconfiguration strategy, MPP candidates are presented in (\ref{mpp}) and number of working modules in MPP candidates are presented in (\ref{qmn}), respectively.

%\begin{equation}
%\begin{aligned}
%\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
%\end{aligned}\label{mpp}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
%\end{aligned}
%\label{qmn}
%\end{equation}
\section{An Algorithm to Identify Feasibility}
In this section, we propose an algorithm to identify feasibility.
\subsection{The Input And Output Of Algorithm}
First, we summarize the input and output of our algorithm. The input of our algorithm is information of a PV array and a configuration. The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate. Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}. For example, this table shows panel P2 includes three, two, and two modules that work in current 0.5A, 2A, and 3A, respectively. Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string. The output of our algorithm is feasibility of the given configuration. That is, the algorithm determines whether there exists assignment of panels to strings that realizes the configuration.
\begin{table}[htbp] 
\caption{Information of a PV array}
\begin{center}
%\begin{equation}
%\begin{center}
\begin{tabular}{l|lllllllll}
    & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & P9 \\ \hline
0.5A & 2  & 3  & 3  & 2  & 2  & 3  & 3  & 3  & 3  \\
 2A & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
 3A & 0  & 2  & 0  & 0  & 0  & 0  & 1  & 0  & 1 
\end{tabular}\label{mpp3-1}
%\end{center}
%\end{equation}
\end{center}
\end{table}  
%\subsection{Feasibility}
%The feasibility of configuration based on the assumption of section \ref{array}, each string in PV array must have same number of panels. Definition of feasibility in (\ref{feas}). When a configuration needs panels in a string (\textit{$NP_n$}) are over maximum number of panels per-string(\textit{$NP_{stMAX}$}) this configuration is unfeasible. 
%\begin{equation}
%\left\{\begin{matrix}
%NP_n > NP_{stMAX}& & \text{Unfeasible}\\ 
%NP_n \leq NP_{stMAX} & & \text{Feasible} 
%\label{feas}
%\end{matrix}\right. 
%\end{equation}
%For the first MPP candidate \{0.5, 0.5, 2\} need 8 modules for each string. According to Table \ref{tab1}, for a string current on 2A at least need 4 panels and didn't meet feasible requirement, thus, algorithm terminate. The second MPP candidate \{0.5, 2, 2\} as same as previous one also not feasible.
Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string. The output of our algorithm is feasibility of the given configuration. That is, the algorithm determines whether there exists assignment of panels to strings that realizes the configuration.
\subsection{Panel Selection Strategy} \label{selection strategy}
Let $s$ be the number of strings, and $i_h$ ($0\le h<s$) be the current assigned to the $h$-th string. Without loss of generality, we assume $i_0\le i_1\le \cdots \le i_{s-1}$ holds. In our algorithm, we first determine the assignment of panels for the $(s-1)$-th string (i.e., the string with the biggest current), and then determine assignments for $(s-2)$-th string, $(s-3)$-th string, and so on.

We explain the way to determine the assignment of the $(s-1)$-th string. To do this, we consider the number of working modules of each panel for currents less than $i_{s-1}$. Let $m_p(i)$ be the number of working modules of Panel $p$ that work in current $i$. For each panel $p$, we consider the difference vector $D_p=(m_p(i_{s-2})-m_p(i_{s-1}), m_p(i_{s-3})-m_p(i_{s-2}), \ldots, m_p(i_0)-m_p(1))$. The first element $d_1$ of $D_p$ means, if we use panel $p$ in current $i_{s-1}$, we lose $d_1$ working modules in current $i_{s-2}$. ... Sorry, I didn't complete this comment.

%Calculate MPP candidates based on existed reconfiguration method in \cite{b10}. MPP current candidates and MPP voltage candidates are present in (\ref{e1}) and (\ref{e2}), respectively. Additional, number of real working module at MPP current candidates are given in (\ref{e3}). Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm in \cite{b10}, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
%\begin{equation}
%\begin{aligned}
%\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
%\end{aligned}
%\end{equation}

 In order to give more precise reconfiguration strategy. Our proposed algorithm firstly sort panels in a particular order for MPP candidates. For the example of fourth MPP candidate \{2, 2, 3\}, by giving dataset in Table \ref{tab1} generate a selection matrix in (\ref{mpp3-1}) that each column indicate panel's number and  each row indicate to string number. Element in the matrix corresponding to number of module which be able to working on string current.

Then calculate number of module difference among string currents. For panel 1, difference between string 3 and string 2 is 1 (\textit{$Diff_1=1$}) and difference between string 2 and string 1 is 0 (\textit{$Diff_2=0$}). Sort panels in lexicographic order by \textit{$Diff_1$} and \textit{$Diff_2$}. As showed in matrix (\ref{sorted}). 
\begin{equation}
\begin{tabular}{l|lllllllll}
        & P2 & P3 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
St1     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
St2     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
St3     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
\textit{$Diff_1$} & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
\textit{$Diff_2$} & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0 
\end{tabular}\label{sorted}
\end{equation}
To find the best PV configuration, following steps are required:
\begin{enumerate} [1-]
\item Select panels in matrix (\ref{sorted}) from left side to right.
\item If the element in matrix is 0, release corresponding panel
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. As the example of string 2, selected panels are [Panel 1, Panel 5], these panels contain modules are equal to next unselect panel [Panel 4]. Then swap [Panel 1, Panel 5] and [Panel4], release [Panel 1, Panel 5]. \label{replace}
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, set unselect panel to a string with minimum length. 
\end{enumerate}
\subsection{Panel Replace Strategy}
In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel. Based on section \ref{array}, each panel only contain three identical PV modules. So the element in selection matrix in the range of 0 to 3. The replacement policy follows priorities are:
\begin{enumerate} [ (1) ]
\item Swap a panel contain 3 working modules to \textbf{three} panels each contain 1 working module.
\item Swap a panel contain 3 working modules to \textbf{one} panel contain 1 working module and \textbf{one} contain 2 working modules.
\item Swap a panel contain 2 working modules to \textbf{two} panels each contain 1 working module.
\end{enumerate}
